COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-08-08 main.tex
Add text to section 2

\section{Collisions and Mean Motion Resonances} \label{sec:dynamics}

@@

\section{Dust Emission} \label{sec:results}

>>>>

\section{Overview of Relavant Dynamics} \label{sec:dynamics}

\subsection{Collisions}

We begin by making the assumption that a typical encounter between planetesimals in a disk is well-described by two-body dynamics. So long as the random velocities of planetesimals $v_{p}$ are large compared to the Hill velocity of a planetesimal $v_{h} = \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role and can be safely ignored. In this case and assuming equal mass bodies, the collision rate is given by \citep{1967SvA....10..650S}

\begin{equation}\label{eq:safronov}
	\sigma v = \pi r_{p}^2 \left( 1 + v_{esc}^2/v_{p}^2 \right) v_{p},
\end{equation}

\noindent where $r_{p}$ is the radius of a planetesimal and $v_{esc}$ is the mutual escape velocity of two planetesimals in contact. The $v_{esc}^2/v_{p}^2$ term describes the factor above which the collision cross section is enhanced due to gravitational focusing. For a dynamically cold planetesimal disk, $v_{p}$ is small relative to $v_{esc}$ and the collision rate becomes strongly enhanced.

In the absence of a proper treatment of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the collision rate in an N-body simulation using only the positions and velocities of particles. This has been done in other studies \citep{2017ApJ...850..103B} (any other examples?), but requires bulk averaging of the phase space properties of particles, which may mask important information and blur out features. We will revisit equation \ref{eq:safronov} in section \ref{sec:results} to test how well the collision rate near mean motion resonances is described by this framework.

\subsection{Mean Motion Resonances}

@@

\section{Dust Emission} \label{sec:dust}
